How Do Like and Dislike Buttons Affect Communication?

### 2020-04-08 analyses/analyses.Rmd
- ms: updates on methods, results, and discussion section

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

@@

```{r SaveData, include=F, cache=F}
write.csv(d, file = "data/data.csv", row.names = FALSE)
save(d, d_raw, d_all, d_fs,
     fit_baseline, fit_prereg, fit_adapted, fit_simple,
     fig_fs_m, fig_fs_cor, fig_coeffs,
     des_pridel,
     model_comp_tab, factor_val_tab,
     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
     n_comments, n_words, n_time, n_posts, n_speeding,
     n_users, n_final,
     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
     n_t1, age_t1_m, male_t1_m, college_t1_m,
     n_t2, age_t2_m, male_t2_m, college_t2_m,
     n_matched, n_final, age_final_m, male_final_m, college_final_m,
     r_sesoi, r_sensitive, power_achieved,
     file = "data/workspace.RData"
     )
```

>>>>

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
```

@@

```{r SaveData, include=F, cache=F}
write.csv(d, file = "data/data.csv", row.names = FALSE)
save(d, d_raw, d_all, d_fs,
     fit_baseline, fit_prereg, fit_adapted, fit_simple,
     fig_fs_m, fig_fs_cor, fig_coeffs,
     des_pridel,
     model_comp_tab, factor_val_tab,
     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
     n_comments, n_words, n_time, n_posts, n_speeding,
     n_users, n_final,
     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
     n_t1, age_t1_m, male_t1_m, college_t1_m,
     n_t2, age_t2_m, male_t2_m, college_t2_m,
     n_matched, n_final, age_final_m, male_final_m, college_final_m,
     r_sesoi, r_sensitive, power_achieved,
     rsquare_fit_prereg, rsquare_fit_adapted, rsquare_fit_simple,
     file = "data/workspace.RData"
     )
```
